### 2016-07-14 version0.0/intro0.0.tex
Update intro0.0.tex
edits to prelude. One question about relation between SFR and SFH.

\section{Prelude}
\label{sec: overview}
%what do we have inside galaxies:
% stuff we don't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas, which all affect each others' formation, evolution and extinction.
There is also dark matter inside every galaxy, which to the best of our knowledge only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their light.
Since each observational phenomenon inside galaxies emits most of its energy in specific wavelengths, 
a plot of brightness/flux density of galaxies as a function of wavelengths, which is called spectral energy distribution (SED), is a useful tool to have a intuition about galaxies. 
Young and evolved stars, dust and gas in the space between the stars are the most important contributors to the spectral energy distributions (SEDs) of galaxies.
We cannot detect any contribution from planets and black holes, the ones without accretion disc, to SEDs due to their low intensity compared to these other components.
Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust and gas inside galaxies.

@@

%ISM 1)Gas 2)dust
%There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas. %: this is a very strong statement. Some galaxies, like dwarf ellipticals, are pretty gas-free (at least now). So qualify this a bit. done
Among observable objects in galaxies, gas has a crucial role in formation and evolution of galaxies.
Gas and dust in galaxies can be found in the space between stars that is called the interstellar medium (ISM). The ISM is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
The effect of the ISM on stellar formation is undeniable;  it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
Studying the interstellar medium is not only essential for understanding of the formation of stars, but also it is necessary for interpretation of stellar evolution in that stars release their material into the ISM when they reach the end of their evolution.

In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$ M$_{\odot})$ in the ISM due to gravitational instabilities. 
The denser regions within GMCs collapse under their own gravity, self-gravity, and creates clumps.
Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF).
Then these clumps continue to become denser and transfer to protostars. 
Since the protostars have higher mass than their surrounding, more gas from GMCs add to protostars.
This procedure continues until hydrogen burning in centre of protostars starts (see~\cite{McKee07} for more detail).

Metallicity, which is defined as the ratio of abundance of metals (any element heavier than hydrogen and helium) to the abundance of hydrogen, affects formation and evolution of stars indisputably.
\cite{Walch11} showed that in the case of large scale turbulence, the effect of metallicity on star formation is negligible, but if turbulence is decaying,  metallicity has a strong impact on stabilizing self-gravitating cores.
Metals also play an important role in heating, cooling and ionizing processes in the ISM.
Since cooling is one of the main reasons for condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed. 
Amount of metals in stars affect their evolutionary tracks~\citep[e.g.][and references therein]{Maeder02}.
For example, low metallicity stars tend to be have lower mass loss by stellar wind than that with higher metallicity.
Since there is lower amount of mass loss in low metallicity stars, hence no loosing angular momentum because of wind, massive low metallicity stars rotate faster.
Being more massive at the end of evolutionary track, makes massive low metallicity stars lower chance to explode (become a supernova).

%what does SED look like?
Our primary source of information for galaxies, specifically unresolved ones, is their spectral energy distributions. 
Broadly speaking, young and hot stars emit most of their light in ultraviolet (UV) wavelengths, evolved stellar populations show themselves in optical and near-infrared (NIR) emission, and gas and dust heated by stellar emission are bright in mid-infrared (MIR) or far-infrared (FIR) wavelengths.
Therefore, UV-to-IR SEDs contain valuable information about galaxies' stellar evolution and their ISM. 
Other wavelengths regimes in galaxy SEDs (i.e. X--ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shocks, are beyond the scope of this thesis.
The general shape of SEDs mirrors the morphological type of galaxies; starburst galaxies, which have high star formation rates (SFRs), emit the bulk of their energy in the UV, while the light of quiescent galaxies is dominated by optical and IR emission. 
Detailed information about the age of stellar populations and other properties of galaxies can be determined by modelling their SEDs.

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
The stellar population synthesis method, which sums stellar spectra of a galaxy to produces its spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A through SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs, (either by minizing $\chi^2$ or by Bayesian analysis)  using the templates.
One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
Some of the physical properties of galaxies should be assumed as an input data to find best SED, and others will be derived from SED results~\citep[See][for more detail]{Walcher08}.
For example, the Best fitted SED has information regarding star formation history and stellar mass to light ratio.
By integrating star formation history over specific time scale, SFR can be derived. 
knowing the stellar mass to light ratio, one can used observed luminosity to calculate stellar mass in galaxies.

Formation of stars in galaxies depends on many parameters, gas, stellar mass, metallicity, dust, galaxy's morphology and location of the star forming region inside the galaxy.
In extragalactic astronomy, measuring the rate that stars form is uncertain and relies upon theoretical models and observational data.
Studying star formation and its relation to other quantities in galaxies in an ongoing progress.
In this chapter, we present a review of observational methods of measuring the star formation rate and the main properties that affect measuring and scaling the SFR. A discussion of the ISM and its role in star formation is presented in $\S$~\ref{sec: ism_intro}. In $\S$~\ref{sec: sfr_intro} we discuss measuring the star formation rate, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{sec: starmass_intro}. Current issues about star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.

>>>>

\section{Prelude}
\label{sec: overview}
%what do we have inside galaxies:
% stuff we don't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas, which all affect each others' formation, evolution and extinction.
There is also dark matter inside every galaxy, which to the best of our knowledge only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their light.
Since each observational phenomenon inside galaxies emits most of its energy in specific wavelengths, 
a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
Young and evolved stars, dust and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
We cannot detect any contribution from planets or non-accreting black holes to SEDs, due to their low intensity compared to these other components.
Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust and gas inside galaxies.

@@

%ISM 1)Gas 2)dust
%There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas. %: this is a very strong statement. Some galaxies, like dwarf ellipticals, are pretty gas-free (at least now). So qualify this a bit. done
Among observable objects in galaxies, gas has a crucial role in the formation and evolution of galaxies.
Gas and dust in galaxies can be found in the space between stars and are together called the interstellar medium (ISM). The ISM is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
The gas and dust in the ISM are heated by interstellar radiation field and cool through a variety of line and continuum processes which usually depend on the local physical conditions. 
The effect of the ISM on stellar formation is undeniable;  it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
Studying the interstellar medium is not only essential for understanding of the formation of stars, but also it is necessary for interpretation of stellar evolution, in that stars release their material into the ISM when they reach the end of their evolution.

In a galaxy like our own, star formation begins with the condensation of giant molecular clouds (GMCs, $\sim 10^7$~M$_{\odot})$ in the ISM due to gravitational instabilities. 
The denser regions within GMCs collapse under their own gravity (self-gravity) and create clumps.
Some of these clumps develop into self-gravitating cores, which have a similar distribution to stellar initial mass function (IMF).
Then these clumps continue to become denser and transfer to protostars. 
Since the protostars have higher mass than their surroundings, more gas from GMCs is added to protostars.
This procedure continues until hydrogen burning starts in the centre of protostars (see~\cite{McKee07} for more details).

Metallicity, which is defined as the ratio of abundance of metals (any element heavier than hydrogen and helium) to the abundance of hydrogen, affects formation and evolution of stars indisputably.
\cite{Walch11} showed that in the case of large scale turbulence, the effect of metallicity on star formation is negligible, but if turbulence is decaying,  metallicity has a strong impact on stabilizing self-gravitating cores.
Metals also play an important role in heating, cooling and ionizing processes in the ISM.
Since cooling is one of the main reasons for condensation of GMCs~\citep[e.g.][]{Maio07}, in low metallicity regions star formation may be suppressed. 
The amount of metals in stars affects their evolutionary tracks~\citep[e.g.][and references therein]{Maeder02}.
For example, low metallicity stars tend to have lower mass loss by stellar winds than those with higher metallicity.
Since there is less mass loss in low metallicity stars, hence no loss of angular momentum because of winds, massive low metallicity stars rotate faster.
Being more massive at the end of their evolutionary track gives massive low metallicity stars a lower chance to explode and become a supernova.

%what does SED look like?
Our primary source of information for galaxies, specifically unresolved ones, is their spectral energy distributions. 
Broadly speaking, young and hot stars emit most of their light in ultraviolet (UV) wavelengths, evolved stellar populations show themselves in optical and near-infrared (NIR) emission, and gas and dust heated by stellar emission are bright in mid-infrared (MIR) or far-infrared (FIR) wavelengths.
Therefore, UV-to-IR SEDs contain valuable information about galaxies' stellar evolution and their ISM. 
Other wavelengths regimes in galaxy SEDs (i.e. X--ray, radio), that are dominated by processes such as active galactic nuclei, quasars, and supernovae shocks, are beyond the scope of this thesis.
The general shape of SEDs mirrors the morphological types of galaxies: starburst galaxies, which have high star formation rates (SFRs), emit the bulk of their energy in the UV, while the light of quiescent galaxies is dominated by optical and IR emission. 
Detailed information about the age of stellar populations and other properties of galaxies can be determined by modelling their SEDs.

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
The stellar population synthesis method, which sums stellar spectra to produce a composite spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A thorough SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs, (either by minizing $\chi^2$ or by Bayesian analysis)  using the templates.
One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
Some of the physical properties of galaxies must be assumed as an input data to find best SED, and others are derived from SED results~\citep[See][for more detail]{Walcher08}.
For example, the best-fit SED has information regarding a galaxy's star formation history and stellar mass to light ratio.
By integrating the star formation history over a specific time scale, the SFR can be derived. %PB: backwards? integrate SFR to get SFH?
Knowing the stellar mass to light ratio, one can use the observed luminosity to calculate stellar mass in galaxies.

The formation of stars in galaxies depends on many parameters, including gas, stellar mass, metallicity, dust, the galaxy's morphology and the location of the star forming region inside the galaxy.
In extragalactic astronomy, measuring the rate that stars form is uncertain and relies upon theoretical models and observational data.
Studying star formation and its relation to other quantities in galaxies in an ongoing progress.
In this chapter, we present a review of observational methods of measuring the star formation rate and the main properties that affect measuring and scaling the SFR. A discussion of the ISM and its role in star formation is presented in $\S$~\ref{sec: ism_intro}. In $\S$~\ref{sec: sfr_intro} we discuss measuring the star formation rate, followed by a discussion of the measurement of the stellar mass in $\S$~\ref{sec: starmass_intro}. Current issues about star formation and its relation to other properties of a galaxy are discussed in $\S$~\ref{sec: pre_intro}.
